---
params: 
    set_title: "My Title!"
    set_author: "My Name!"
title: "`r params$set_title`"
subtitle: Interim Analysis for Futility Using Bayesian Predictive Probability
date: "`r format(Sys.time(), '%d %B %Y')`"
author: "`r params$set_author`"
header-includes: 
    - \usepackage{bbm}
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage[table]{xcolor}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
---
 
 ======================================================== 

```{r library, echo = FALSE,comment = "",warning = FALSE,message = FALSE}

library(shiny)
library(knitr)
library(rmarkdown)
library(kableExtra)
library(extraDistr)

options(scipen = 3)
#options(knitr.table.format  =  "latex")
```


```{r set-options, echo = FALSE, cache = FALSE}
options(width = 60)
opts_chunk$set(comment  =  "", warning  =  FALSE, message  =  FALSE, echo  =  TRUE, tidy  =  FALSE, size = "small",fig.height = 5)

```



```{r output type, echo = FALSE, cache = FALSE}
output_type <- switch(opts_knit$get("rmarkdown.pandoc.to"),
                      docx = 'pandoc',
                      latex = 'latex',
                      html = 'html'
)
```

```{r, echo = FALSE}
tmp99  <-   get.result.futility()

if (tmp99$pH1 > tmp99$pTarget)
  increase <- TRUE else
    increase <- FALSE

if (ncol(tmp99$sensitivity.data.ind) >= 3) 
  run_fig_3 <- TRUE else
    run_fig_3 <- FALSE

```

# Summary of Interim Analysis for Futility 

```{r, echo = FALSE, results = 'asis'}
cat(tmp99$a1_summary)
```

## Details

```{r, echo = FALSE, results = 'asis'}
cat(tmp99$a1)
```

# Table 1: Stopping Boundary for Futility

```{r, echo = FALSE, results = 'asis'}
 
    aa0 <- tmp99
    aa <- aa0$n.list
    cutoff.tmp <- c(aa0$n.predictive.cutoff,aa0$n.needed.for.greater.p0 - 1)
    cutoff.tmp[cutoff.tmp == (-99)] <- 'PASS'
    aa <- rbind(c(1:(length(aa) - 1),'Final'),cumsum(aa),aa,cutoff.tmp)
    dimnames(aa)[[1]] <- c('Stage of interim analysis','Sample size up to the current stage','Sample size at each stage','Stopping boundary')
    kable(aa, format = output_type)
  
``` 
 
# Table 2: Bayesian Predictive Probability for Stopping Rule

```{r, echo = FALSE, results = 'asis'}
#library(dplyr)
    aa0 <- tmp99
    aa.list <- aa0$predictive.prob.data
      
    for (my_j in 1:length(aa.list))
    {
      stage.index <- ifelse(my_j == 1,' 1st ',ifelse(my_j == 2,' 2nd ',ifelse(my_j == 3,' 3rd ',paste(' ',my_j,'th ',sep = ''))))
      aa <- aa.list[[my_j]][,3:5,drop = F]
      aa[,dim(aa)[2]] <- round(aa[,dim(aa)[2]],3)
      outcomeLabel <- aa0$outcomeLabel
      dimnames(aa)[[2]] <- c(paste('number of patients with ', outcomeLabel,' in the ',stage.index,' interim analysis',sep = ''),paste(ifelse(increase, 'minimum', 'maximum'), ' number of patients with ',outcomeLabel,' ',ifelse(aa0$increase, 'needed', 'allowed'),' in the future remaining patients',sep = ''),'predictive probability')
      print(kableExtra::kable(aa, format = output_type) %>% column_spec(1:3, width = c("12em","12em","6em")))

    }
    
```

# Table 3: Performance (Probability of Early Termination, Type I error, and Power) 

```{r, echo = FALSE, results = 'asis'}

    aa <- tmp99$sensitivity.data
    outcomeLabel <- tmp99$outcomeLabel
    aa <- cbind(as.numeric(dimnames(aa)[[1]]),aa)
    dimnames(aa)[[2]] <- c('true rate',' overall probability of early stopping the trial',paste('probability to have at ',ifelse(increase, 'least', 'most'),' ',aa0$n.needed.for.greater.p0,' patients with ',aa0$outcomeLabel,sep = ''))
  kable(aa, format = output_type, row.names = FALSE, digits = c(2,3,3)) %>% column_spec(1:3, width = c("6em","10em","10em"))
  
    
```

# Table 4: Sensitivity Analysis: Predictive Probability

```{r, echo = FALSE, results = 'asis'}
    aa <- round(tmp99$sensitivity.analysis.ans$predictive.prob$ans,2)
    kable(aa, format = output_type)
    
```

# Table 5: Sensitivity Analysis: Posterior Probability

```{r, echo = FALSE, results = 'asis'}
    aa <- round(tmp99$sensitivity.analysis.ans$posterior.prob$ans,2)
    kable(aa, format = output_type)

```


# Table 6: Sensitivity Analysis: Sample Size

```{r, echo = FALSE, results = 'asis'}
    aa <- round(tmp99$sensitivity.analysis.ans$sample.size$ans,2)
    kable(aa, format = output_type)

```

# Table 7: Sensitivity Analysis: Beta Prior Distribution

```{r, echo = FALSE, results = 'asis'}
    aa <- round(tmp99$sensitivity.analysis.ans$prior$ans,2)
    kable(aa, format = output_type)

```


# Figure 1: Bayesian Predictive Probability for Stopping Rule

```{r, echo = FALSE, results = 'asis',fig.height = 12,fig.width = 16,dpi = 600}

  res  <-   tmp99
  n.list <- res$n.list
  pTarget <- res$pTarget
  theta <- res$theta
  predictive.cutoff <- cutoffPredictive <- res$cutoffPredictive
  outcomeLabel <- res$outcomeLabel
  armLabel <- res$armLabel
  betaA <- res$betaA
  betaB <- res$betaB
  kk2.len.list <- res$kk2.len.list
  n.predictive.cutoff.list <- res$n.predictive.cutoff
  tmp3.list <- res$predictive.prob.data
  org_mar <- par()$mar
  par(mar = c(5.1, 4.1, 8.1, 2.1))
    for (my_j in 1:length(tmp3.list)) {
      tmp3 <- tmp3.list[[my_j]]
      n1 <- sum(n.list[1:my_j])
      n2 <- sum(n.list[(my_j + 1):length(n.list)])
      kk2.len <- kk2.len.list[[my_j]]
      n.predictive.cutoff <- n.predictive.cutoff.list[my_j]
      stage.index <- ifelse(my_j == 1,' 1st ',ifelse(my_j == 2,' 2nd ',ifelse(my_j == 3,' 3rd ',paste(' ',my_j,'th ',sep = ''))))

        plot(tmp3[,5],type = 'h',axes = F,xlab = paste('number of patients with ', outcomeLabel,' in the',stage.index,' interim analysis with ',n1,' patients',sep = ''),ylab = 'predictive probability',lwd = 3,cex.lab = 2, cex.main  = 5, cex.axis = 2)
        box();axis(2,cex.axis = 2)
        axis(4,predictive.cutoff,cex.axis = 2)
        axis(1,1:dim(tmp3)[1],tmp3[,3],cex.axis = 2)
        axis(3,1:dim(tmp3)[1],tmp3[,4],cex.axis = 2)
        abline(h = predictive.cutoff,col = 2,lty = 2)
        mtext(paste(stage.index,' Interim Analysis of for Futility \n', ifelse(increase, 'minimum', 'maximum'),' number of patients with ',outcomeLabel,' ',ifelse(increase, 'needed', 'allowed'),' in the future remaining ', n2,' patients \n',sep = ''),side = 3,line = 1.8, cex = 2)
        # title(paste(stage.index,' Interim Analysis of for Futility \n\n',sep = ''))
        arrows(kk2.len, 1, kk2.len, y1  =  0.1,col = 3,lwd = 3)
        text(1:dim(tmp3)[1],tmp3[,5],round(tmp3[,5],2),col = 2,cex = 2)
        
        if (length(tmp3.list) > 1) cat('\r\n\r\n')
  }
  par(mar = org_mar)
```

# Figure 2: Performance (Probability of Early Termination (PET), Type I error, and Power)

```{r, echo = FALSE, results = 'asis',fig.height = 14,fig.width = 14,dpi = 600}
    res  <-   tmp99
    tmp5 <- res$sensitivity.data
    tmp5.ind <- res$sensitivity.data.ind
    n.list <- res$n.list
    pTarget <- res$pTarget
    theta <- res$theta
    cutoffPredictive <- res$cutoffPredictive
    outcomeLabel <- res$outcomeLabel
    armLabel <- res$armLabel
    betaA <- res$betaA
    betaB <- res$betaB
    n.predictive.cutoff <- res$n.predictive.cutoff
    n.needed.for.greater.p0 <- res$n.needed.for.greater.p0
    
    par(mfrow = c(2,1))
    aa1 <- barplot(tmp5[,1],xlab = paste('Rate of ',outcomeLabel,sep = ''),ylab = 'Probability of early stopping the trial overall',main = 'Overall probability of early stopping the trial (PET)',lwd = 3,cex.lab = 1.5,ylim = c(0,1),cex.main = 2,cex.lab = 1.5,cex.axis = 1.5,cex = 1.5)
    text(aa1,pmin(tmp5[,1] + .1, .95),round(tmp5[,1],2),col = 2,cex = 2)
    
    aa1 <- barplot(tmp5[,2],xlab = paste('Rate of ',outcomeLabel,sep = ''),ylab = paste('Probability of at ',ifelse(increase, 'least', 'most'),' ', n.needed.for.greater.p0,' patients with ', outcomeLabel,sep = ''),main = paste('Probability of at ',ifelse(increase, 'least', 'most'),' ', n.needed.for.greater.p0,' patients with ',outcomeLabel,sep = ''),lwd = 3,cex.lab = 1.5,ylim = c(0,1),cex.main = 2,cex.lab = 1.5,cex.axis = 1.5,cex = 1.5)
    text(aa1,pmin(tmp5[,2] + .1, .95),round(tmp5[,2],2),col = 2,cex = 2)
    par(mfrow = c(1,1))


```

`r if (run_fig_3) '# Figure 3: Probability of Early Stopping  by Each Interim Analysis'`

```{r, echo = FALSE, results = 'asis',fig.height = 12,fig.width = 14,dpi = 600, eval = ifelse(run_fig_3,T,F)}
    res  <-   tmp99
    tmp5 <- res$sensitivity.data
    tmp5.ind <- res$sensitivity.data.ind
    n.list <- res$n.list
    pTarget <- res$pTarget
    theta <- res$theta
    cutoffPredictive <- res$cutoffPredictive
    outcomeLabel <- res$outcomeLabel
    armLabel <- res$armLabel
    betaA <- res$betaA
    betaB <- res$betaB
    n.predictive.cutoff <- res$n.predictive.cutoff
    n.needed.for.greater.p0 <- res$n.needed.for.greater.p0
    
    dim.n <- dim(tmp5.ind)[2]
    
      for (my_j in 1:(dim.n - 1))
      {
        aa1 <- barplot(tmp5.ind[,my_j],xlab = paste('Rate of ',outcomeLabel,sep = ''),ylab = paste('Probability of early stopping the trial at interim',my_j),main = paste('Interim Analysis: ',my_j,'\n Probability of early stopping the trial',sep = ''),lwd = 3,cex.lab = 1.5,ylim = c(0,1),cex.main = 2,cex.lab = 1.5,cex.axis = 1.5,cex = 1.5)
        text(aa1,pmin(tmp5.ind[,my_j] + .1,.95),round(tmp5.ind[,my_j],2),col = 2,cex = 2)
        
        if ((dim.n - 1) > 1) cat('\r\n\r\n')
      }
```


# Figure 4: Sensitivity Analysis: Predictive Probability

```{r, echo = FALSE, results = 'asis',fig.height = 24,fig.width = 18,dpi = 600}
    res  <-   tmp99
    aa0<-res$sensitivity.analysis.ans$predictive.prob
    tmp0<-aa0$ans
    var.name.tmp<-aa0$var.name.tmp

    par(mfrow=c(3,1))
    name2<-c('PET','typeI','power')
    name21<-c('PET','type I error','power')
    for(i in 1:length(name2))
    {
      plot(1:dim(tmp0)[1],tmp0[,name2[i]],xlab=var.name.tmp,ylab=name21[i],main=name21[i],axes=F,cex.axis=4,cex.main=6,cex=3,cex.lab=2)
      box()
      axis(2,cex.axis=3)
      axis(1,1:dim(tmp0)[1],tmp0[,var.name.tmp],cex.axis=3)
      index1<-tmp0[,1]==res$theta
      points((1:dim(tmp0)[1])[index1],tmp0[index1,name2[i]],col=2,cex=5,pch=2)

    }

    ```

# Figure 5: Sensitivity Analysis: Posterior Probability

```{r, echo = FALSE, results = 'asis',fig.height = 24,fig.width = 18,dpi = 600}
    res  <-   tmp99
    aa0<-res$sensitivity.analysis.ans$posterior.prob
    tmp0<-aa0$ans
    var.name.tmp<-aa0$var.name.tmp

    par(mfrow=c(3,1))
    name2<-c('PET','typeI','power')
    name21<-c('PET','type I error','power')
    for(i in 1:length(name2))
    {
      plot(1:dim(tmp0)[1],tmp0[,name2[i]],xlab=var.name.tmp,ylab=name21[i],main=name21[i],axes=F,cex.axis=4,cex.main=6,cex=3,cex.lab=2)
      box()
      axis(2,cex.axis=3)
      axis(1,1:dim(tmp0)[1],tmp0[,var.name.tmp],cex.axis=3)
      index1<-tmp0[,1]==res$theta
      points((1:dim(tmp0)[1])[index1],tmp0[index1,name2[i]],col=2,cex=5,pch=2)

    }

    ```

# Figure 6: Sensitivity Analysis: Sample Size

```{r, echo = FALSE, results = 'asis',fig.height = 24,fig.width = 18,dpi = 600}
    res  <-   tmp99
    aa0<-res$sensitivity.analysis.ans$sample.size
    tmp0<-aa0$ans
    var.name.tmp<-aa0$var.name.tmp
    par(mfrow=c(3,1))
    name2<-c('PET','typeI','power')
    name21<-c('PET','type I error','power')
    for(i in 1:length(name2))
    {
      plot(1:dim(tmp0)[1],tmp0[,name2[i]],xlab='sample size',ylab=name21[i],main=name21[i],axes=F,cex.axis=4,cex.main=6,cex=3,cex.lab=2)
      box()
      axis(2,cex.axis=3)
      nn1<-apply(tmp0[,var.name.tmp],1,paste,collapse='/')
      axis(1,1:dim(tmp0)[1],nn1,cex.axis=3)
      index1<-nn1==paste(res$n.list,collapse ='/')
      points((1:dim(tmp0)[1])[index1],tmp0[index1,name2[i]],col=2,cex=5,pch=2)
    }

    ```

# Figure 7: Sensitivity Analysis: Beta Prior Distribution

```{r, echo = FALSE, results = 'asis',fig.height = 24,fig.width = 18,dpi = 600}
    res  <-   tmp99
    aa0<-res$sensitivity.analysis.ans$prior
    tmp0<-aa0$ans
    var.name.tmp<-aa0$var.name.tmp
    beta.prior.list<-c(res$betaA,res$betaB)

    par(mfrow=c(3,1))
    name2<-c('PET','typeI','power')
    name21<-c('PET','type I error','power')
    for(i in 1:length(name2))
    {
      plot(1:dim(tmp0)[1],tmp0[,name2[i]],xlab='prior distribution: beta.a/beta.b or response rate (SD)',ylab=name21[i],main=name21[i],axes=F,cex.axis=4,cex.main=6,cex=3,cex.lab=2)
      box()
      axis(2,cex.axis=3)
      nn1<-apply(round(tmp0[,1:2],2),1,paste,collapse='/')
      axis(1,1:dim(tmp0)[1],dimnames(tmp0)[[1]],cex.axis=3)
      index1<-nn1==paste(beta.prior.list,collapse ='/')
      points((1:dim(tmp0)[1])[index1],tmp0[index1,name2[i]],col=2,cex=5,pch=2)
    }

    ```
    
    

# References 

`r tmp99$a2[1]`

`r tmp99$a2[2]`
